\chapter{Methodology}

	In other to achieve the goals of this project the endeavours were divided into three 

	\section{Lieterature Review}
		This stage can be considered the most important of the whole project because it layers the foundations for development of all that follows. This stage comprehended the knowledge needed in all further stages and steps of the project, even on the further stages of development it was necessary to review some of the information acquired on this part in other to achieve best results. On the Literature Review stage, concepts, components and other necessary information to make the foundations for the project were adressed. For instance it will be on this stage that the brake tests parameters and requirements will be analysed in order to choose the proper solutions for this project.

	\section{Problem Description}
		This particular stage consisted on the depuration of the problem in question, leading to a study of the requirements that were necessary to ensure in other to develop and execute the project. 

	\section{Project Conception}
		After a deep problem analysis it was possible to adress a more detailed solution description, in this stage the general solution was splitted in many smaller ones that were defined according to the requirements of the previous stage. All this solutions were focused in functionality, this is a project of electronic instrumentation, so the goal was not to develop electrical/electronic solutions from the beggining, it was evaluating the requirements and finding a group of components/solutions that combined in a particular and unique way could lead to this project achieving it's goals.
		
	\section{Case Study}
		After the particular and smaller solutions are developed, tested and considered functional, the general solution of this project will be tested as a whole thing. This being doing a brake test that is capable of proving the functionality and usability of the developed technology.
